### 2013-07-24 doc/dissertation/document/frontmatter/acks.tex
adding summary sections in cconclusion chapter

Great thanks are owed to my advisor and friend Paul Wilson for
providing me years of guidance and the opportunity to develop this
work. Without him, this work would have never been possible.

Tom Evans is responsible for presenting me with the seeds of this work
and for that I thank him. His mentoring over the past few years has
been invaluable.

Roger Pawlowski and other members of the Consortium for Advanced
Simulation of Light Water Reactors and Trilinos teams as well as many
staff members at Oak Ridge National Laboratory have provided
tremendous resources for my professional and technical development and
have greatly facilitated this work.

@@

>>>>

@@

Thank you to the Oak Ridge Leadership Computing Facility (OLCF) for
providing computational resources and support.
